### 2017-05-24 2017mergingmerges/section/05-Evaluation.tex
benchmark: put us first
Add Conduit Quickhull runtime as comment
Not sure what to do: showing Conduit runtimes makes difference between
Folderol and Vector insignificant.
split out bench figure to separate file

% In general, the @drop@ for a particlar stream should be placed just before a @pull@ from the same stream.

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
  symbolic x coords={Append, Partition, Quickhull, end},
        ylabel=Runtime (ms),
  ymin=0, ymax=300,
        enlargelimits=0.01,
        ybar interval=0.8,
  width=8.0cm, height=4.5cm,
  legend style={at={(0.5,-0.2)},anchor=north, legend columns=3}
]
\addplot coordinates {(Append,  88) (Partition,  60) (Quickhull, 126) (end, 0) };
\addplot coordinates {(Append,  86) (Partition,  61) (Quickhull, 202) (end, 0) };
\addplot coordinates {                               (Quickhull, 274) (end, 0) };
\addplot coordinates {(Append, 282) (Partition, 136) (Quickhull,   0) };
\addplot coordinates {(Append, 270) (Partition, 166) (Quickhull,   0) };
\addplot coordinates {(Append, 168) (Partition, 268) (Quickhull,   0) };
\addplot coordinates {(Append, 0)   };
\legend{Handfused, Ours, Vector, Conduit, Pipes, Streaming}
\end{axis}
\end{tikzpicture}
\caption{Runtime for benchmarks; lower is faster.}
\label{fig:bench:all}
\end{figure}

% Quickhull
% \addplot coordinates {(200,Store) (130,Recompute) (110,Ours) (75,Hand) (0,end) };
% Append
% \addplot coordinates {(282,Conduit) (270,Pipes) (168,Streaming) (86,Ours) (0,end) };
% Partition
% \addplot coordinates {(1200,Streaming) (764,Pipes) (658,Conduit hand) (288,Ours) (0,end) };

>>>>

% In general, the @drop@ for a particlar stream should be placed just before a @pull@ from the same stream. 
\input{figures/bench.tex}
